---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  out.width = "100%",
  tidy = "styler"
)
library(knitr)
library(patentsview2)
library(tidyverse)
library(styler)
data("cpc_subclasses")
```

# patentsview2

`patentsview2` is a simple set of functions to query the [Patent endpoint](https://search.patentsview.org/docs/docs/Search%20API/EndpointDictionary/#patent) of the [PatentsView API](https://patentsview.org/) using [CPC Subclass](https://en.wikipedia.org/wiki/Cooperative_Patent_Classification) identifiers (e.g. [G16H for medical informatics](https://www.uspto.gov/web/patents/classification/cpc/html/cpc-G16H.html#G16H)).

As promised, this package was reworked to use the new version of the
Patentsview API (renamed the PatentSearch API, as
 announced [here](https://search.patentsview.org/docs/#naming-update)).
We're also using the [updated patentview R package](https://mustberuss.github.io/patentsview/) though it's not on 
CRAN yet.  

# introduction

Patents and patent applications are a valuable measure of innovation within countries, sub-national geographies (e.g. states or cities), industries, and firms. Numerous patent databases exist, including [PATSTAT from the EPO](https://data.epo.org/expert-services/index.html), [NBER](https://www.nber.org/research/data/us-patents), [Google Patents](https://patents.google.com/), [OECD Patent Microdata](https://www.oecd.org/sti/intellectual-property-statistics-and-analysis.htm), [the USPTO](https://www.uspto.gov/patents/search), and [others](https://iii.pubpub.org/datasets). These databases can be unweildy, so the USPTO created [PatentsView](https://patentsview.org/home) as a user-friendly query portal for data about individual patents. They also implemented several API endpoints that can be queried directly. Despite its public availability and documentation, the PatentsView API isn't *that* easy to use. So to collect data about patents across different patent types, classified by Cooperative Patent Classification (CPC) subclasses, I wrote a few helper functions. Hope they're useful.

# installation steps

1. API team now requires an API key so you'll need to 
[request one](https://patentsview-support.atlassian.net/servicedesk/customer/portals) before any of this will work.
The new version of the patentsview R package looks for its value in the environmental
variable PATENTSVIEW_API_KEY.  Please be careful when posting scripts to not include the value of your API key.

2. Install the new version of the Patentsview R package from r-universe
    ```{r eval = FALSE}
    install.packages("patentsview", repos = c("https://mustberuss.r-universe.dev"))
    ```

3. Install the dev version of this package, patentsview2, from github
    ```{r eval = FALSE}
    if (!"devtools" %in% rownames(installed.packages())) {
      install.packages("devtools")
    }

    devtools::install_github("nateapathy/patentsview2")
    ```

# the `patents_view()` function

`patentsview2::patents_view()` is the primary function. This function calls two other functions, `pv_post()` and `clean_patents()`. This function has a single argument, `cpc`, which takes a string consisting of any of the  4-character CPC subclasses available in PatentsView. By default, the function returns all patent applications with the defined classification since Jan 1, 2001 to the USPTO by US-based assignees.
The earliest patent application in the database is 200100000012

```{r}
library(patentsview2)

patents_view(cpc="F03B")
```

This returns a data frame of patent application observations and 30 fields of information about the patent as well as the inventors and assignees.

## `pv_post()` and `clean_patents()`

You should not have to call either of these functions directly. Both are called by `patents_view()` to help with constructing the POST call to the API and to clean up the data frame, as their names imply.

# the CPC datasets

The package also includes two data sets for reference to CPC subclasses. `cpc_subgroups` lists all subclasses, groups, and subgroups (258,827 observations), while `cpc_subclasses` lists only the four-character subclass codes (615 observations) that can be used in the `cpc` argument within `patents_view()`.

```{r}
data("cpc_subclasses") # 615 obs by 2 vars
data("cpc_subgroups") # 258,827 obs by 5 vars
```

Use `cpc_subclasses` to find subclasses of interest, and use the 4-character code found in the `cpc_subclass` field in your query. You can also [browse the CPC hierarchy from the USPTO](https://www.uspto.gov/web/patents/classification/cpc/html/cpc.html). You may also want to loop through several CPC subclasses, as below. Note that the below code does not look for patents with all subclasses, but rather performs distinct API calls for each of the 5 random CPC subclasses sampled. In this case, the 5 data frames will all be in the `random_cpcs` list.

```{r}
# random sample of CPCs
cpc_samp <- sample(cpc_subclasses$cpc_subclass,5)
random_cpcs <- list()
for (i in c(1:length(cpc_samp))) {
  random_cpcs[[i]] <- patents_view(cpc=cpc_samp[i])
}
names(random_cpcs) <- cpc_samp
```

# an example

```{r, eval=T}
# CPC Subclass B62K: Unicycles
cpc_subclasses %>% filter(cpc_subclass=="B62K")
b62k <- patents_view(cpc="B62K")
dim(b62k) 
# patent applications since Jan 1 2000

# get number of unique patient numbers
# remember, each observation is an APPLICATION not a patent
unique(b62k$patent_number) %>% length() 

# how many unique first assignees?
unique(b62k$assignee_organization) %>% length() 

# what other fields do we have?
colnames(b62k)

# where are unicycle patent applications concentrated?
b62k %>% 
  group_by(inv_city_state) %>% 
  tally() %>% 
  arrange(desc(n)) %>% 
  ungroup() %>%
  mutate(pct=n/sum(n)*100,
         cumulative_pct=cumsum(pct)) %>%
  top_n(10,n) %>% kable()
```

And now that we are using the patentsview R package, we can do other interesting
things like figuring out which of the applications in B62K have become patents.
This can potentially change every time we run this query as more and more
patent applications become issued patents and as new applications are classified
with a subclass of B62K.

(Functions to do the post and clean below could be added to this package!)

```{r, eval=T}
  # Granted patent data is available from the API for 1976 onward,
  # as it was in the original version of the API.  With the new
  # version of the API, application data is also available for 2001 onward.  

  # Here we'll make a query to the new publication endpoint with functionally 
  # the same parameters as pv_post() makes to the patent endpoint
  application_query <- patentsview::with_qfuns(
    and(
      gte(publication_date = "2001-01-01"),
      eq(cpc_current.cpc_subclass_id = "B62K"),
      eq(assignees.assignee_country = "US")
    )
  )

  fields_to_return <- c("assignees", "inventors", "cpc_at_issue")
  patent_applications <- patentsview::search_pv(application_query, endpoint = "publication", fields = fields_to_return, all_pages = TRUE)
  nrow(patent_applications$data$publications)
  unnested <- patentsview::unnest_pv_data(patent_applications$data)
  unnested

  # The new version of the API does not have publication_firstnamed_inventor_city
  # or publication_firstnamed_inventor_state so we'll getting them from
  # the first inventor (inventor_sequence of zero)

  # document_number is a string in inventors and numeric in publications
  # first inventor: min(unnested[["inventors"]]$inventor_sequence) is 0
  first_inventors <- unnested[["inventors"]] %>%
    dplyr::filter(inventor_sequence == 0) %>%
    dplyr::mutate(inv_city_state = paste0(inventor_city, ", ", ifelse(is.na(inventor_state), inventor_country, inventor_state))) %>%
    dplyr::mutate(document_number = as.numeric(document_number))

  # document_number is a string in assignees and numeric in publications
  # first assignee: min(unnested[["assignees"]]$assignee_sequence) is 1
  first_assignees <- unnested[["assignees"]] %>%
    dplyr::filter(assignee_sequence == 1) %>%
    dplyr::mutate(document_number = as.numeric(document_number))

  publications <- unnested[["publications"]] %>%
    dplyr::inner_join(first_inventors,  by = "document_number") %>%
    dplyr::left_join(first_assignees,  by = "document_number")

  dim(publications)
  colnames(publications)
```

There's more information on the patentsview R package [here](https://github.com/ropensci/patentsview) (not yet updated for the new verion)

